Distinguishing Spin-Aligned and Isotropic Black Hole Populations With Gravitational Waves

### 2017-06-02 paper/AlignedIsotropicGW.tex
Close #49, too many 'are's.
Close #50, typo in chi_1 chi_2 bounds.

Observational data on spin magnitudes in black hole systems is
sparse\cite{2015PhR...548....1M}.  Most of the systems studied are
low-mass X-ray binaries rather than the high-mass X-ray binaries that
are likely to be the progenitors of double black hole binaries.  In
addition, there are substantial systematic errors that can complicate
these analyses\cite{2015PhR...548....1M} and selection effects could
yield a biased distribution. Nonetheless, if we take the reported spin
magnitudes as representative then we find that there is a preference
for high spins; for example, 14 of the 19 systems with reported spins
have dimensionless spin parameters in excess of 0.5.  It is usually
argued that the masses and spin parameters of stellar-mass black holes
are unlikely to be altered significantly by
accretion\cite{1999MNRAS.305..654K}, but this may not be true for all
systems\cite{2003MNRAS.341..385P,2015ApJ...800...17F}.  Thus the
current spin parameters are probably are close to their values upon
core collapse, at least in high-mass X-ray binaries.  However, the
specific processes involved in the production of black hole binaries
from isolated binaries could alter the spin magnitude distribution of
those holes relative to the X-ray binary systems; for example, close
tidal interactions could spin up the core, or stripping of the
envelope could reduce the available angular
momentum\cite{2016MNRAS.462..844K,2017arXiv170200885Z,2017arXiv170203952H}.

@@

The effective spin is defined by\cite{2016PhRvL.116x1102A} 
\begin{equation}
  \chieff = \frac{c}{GM} \left( \frac{\vec{S}_1}{m_1} + \frac{\vec{S}_2}{m_2}
  \right) \cdot \frac{\vec{L}}{\left| \vec{L} \right|} \equiv \frac{1}{M} \left( m_1 \chi_1 + m_2 \chi_2 \right),
\end{equation}
where $m_{1,2}$ are the gravitational masses of the more-massive (1)
and less-massive (2) components, $M = m_1 + m_2$ is the total mass,
$\vec{S}_{1,2}$ are the spin angular momentum vectors of the black
holes in the binary, $\vec{L}$ is the orbital angular momentum vector,
assumed to point in the $\hat{z}$ direction, and
$0 \leq \chi_{1,2} \leq 1$ are the corresponding dimensionless
projections of the individual \ac{BH} spins.  Because the
dimensionless spin parameter,
\begin{equation}
  \label{eq:a-def}
  a_{1,2} = \frac{c}{G m_{1,2}^2} \left|\vec{S}_{1,2} \right|,
\end{equation}
of each black hole is bounded by $0 \leq a_{1,2} < 1$, the projections
along the orbital axis are bounded by $-1 < \chi_{1,2} < 1$, and
$-1 < \chieff < 1$.

>>>>

Observational data on spin magnitudes in black hole systems is
sparse\cite{2015PhR...548....1M}.  Most of the systems studied are
low-mass X-ray binaries rather than the high-mass X-ray binaries that
are likely to be the progenitors of double black hole binaries.  In
addition, there are substantial systematic errors that can complicate
these analyses\cite{2015PhR...548....1M} and selection effects could
yield a biased distribution. Nonetheless, if we take the reported spin
magnitudes as representative then we find that there is a preference
for high spins; for example, 14 of the 19 systems with reported spins
have dimensionless spin parameters in excess of 0.5.  It is usually
argued that the masses and spin parameters of stellar-mass black holes
are unlikely to be altered significantly by
accretion\cite{1999MNRAS.305..654K}, but this may not be true for all
systems\cite{2003MNRAS.341..385P,2015ApJ...800...17F}.  Thus the
current spin parameters are probably close to their values upon core
collapse, at least in high-mass X-ray binaries.  However, the specific
processes involved in the production of black hole binaries from
isolated binaries could alter the spin magnitude distribution of those
holes relative to the X-ray binary systems; for example, close tidal
interactions could spin up the core, or stripping of the envelope
could reduce the available angular
momentum\cite{2016MNRAS.462..844K,2017arXiv170200885Z,2017arXiv170203952H}.

@@

The effective spin is defined by\cite{2016PhRvL.116x1102A} 
\begin{equation}
  \chieff = \frac{c}{GM} \left( \frac{\vec{S}_1}{m_1} + \frac{\vec{S}_2}{m_2}
  \right) \cdot \frac{\vec{L}}{\left| \vec{L} \right|} \equiv \frac{1}{M} \left( m_1 \chi_1 + m_2 \chi_2 \right),
\end{equation}
where $m_{1,2}$ are the gravitational masses of the more-massive (1)
and less-massive (2) components, $M = m_1 + m_2$ is the total mass,
$\vec{S}_{1,2}$ are the spin angular momentum vectors of the black
holes in the binary, $\vec{L}$ is the orbital angular momentum vector,
assumed to point in the $\hat{z}$ direction, and
$-1 \leq \chi_{1,2} \leq 1$ are the corresponding dimensionless
projections of the individual \ac{BH} spins.  Because the
dimensionless spin parameter,
\begin{equation}
  \label{eq:a-def}
  a_{1,2} = \frac{c}{G m_{1,2}^2} \left|\vec{S}_{1,2} \right|,
\end{equation}
of each black hole is bounded by $0 \leq a_{1,2} < 1$, the projections
along the orbital axis are bounded by $-1 < \chi_{1,2} < 1$, and
$-1 < \chieff < 1$.
